---
title: "W_UP_01"
author: "Shauna Breazeal"
date: "20 Jan 2021"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable is number of push ups in 2 minutes, the explanatroy variable is position: line, or skill.  
We will use numeric ~ categorical


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
### Plot boxplots

```{r}
boxplot(pushups~position,data=mydata)
```
This box plot shows that the skill players seem to be able to do more pushups in 2 minutes than the line players


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=mydata)
```
The numerical results show that the skill position players median number of pushups in 2 minutes is more than double that of the line position players.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


  
```{r}
t.test(pushups~position,data=mydata)
```
The p-value is 0.0000009; thus $H_0$ is highly unlikely; we reject the null hypothesis
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was, "Do players on the football team in line and skill positions do on average the same number of pushups in 2 minutes?"

Both the graphical and numerical summaries showed the skill position players did, on average, more pushups in 2 minutes than did the line players.

And the result is significant; too unlikely to have occurred by chance; we conclude that at least for Georgetown players the skill position players do more pushups. 